A graph-based data model for interactive evolutionary computation

### 2017-01-20 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Smaller figures

  \item {\bf User-User}

  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user\'s preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users\' preferences.

@@

\begin{figure*}[h!tbp]
\captionsetup{justification=centering,margin=2cm}
\centering
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.7pt}
\fbox{\includegraphics[width=12cm,height=10cm,keepaspectratio]{img/UI_ed01.png}}
\caption{User interface of an EvoSpace-Interactive application.}
\label{fig:web}       
\end{figure*}

\subsection{EvoSpace-Interactive}
\label{sec:evospace-i} 
As a case study, a IEA was implented using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the aplication is presented next, focusing
on the data elements that where ported to the graph model.

@@

\subsubsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend\'s collections by using the web interface depicted 
in Figure \ref{fig:web}

At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
He can assign a quality assessment to the individual using
a five star rating measure.
Additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special directory to store individuals a user prefers and wishes
to save. After the user finishes interacting the individual
on the Wall, he can choose to retrieve a new one from population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=8cm,keepaspectratio]{img/framework.png}

  \caption{Human-Centerd Framework.}
  \label{fig:uc_framework}       
\end{figure}

@@

\begin{itemize}
  \item Interactive Evolutionary Computational system. 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the posibility that fitness or even part of the search 
  to be done by devices lended by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item IEC Data Model.
  A data model is used to describe the IEC system prior to a physical 
  implementation. 
  %% This block is maybe not needed but in our ES-I implementation
  %% we use Relational (PosgreSQL), Objects (JSON-Redis) and Graphs (Neo4J)
  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a Class Digram for a 
  key-value store. 
  %%
  %%
  A graph is proposed for modelling the social network
  of users and their interaction with the population. This database 
  is the back-end of the system, is used by the EA and the user interface.

  \item Evolutionary Algorithm. 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physicaly created
  the new population.  
\end{itemize}

@@

\subsection{Relationships Type}
%%
%% Explain relations

@@

The relation {\tt knows} connects two users that know each other. This relation
is "unique" meaning that it can not be repeted between a pair of nodes.

The relation {\tt parent} describes what Individual is the parent of a new
Individual and is also unique.

The relation {\tt has} describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  individuals stored
in them.

In figure \ref{fig:Has_edge} the edge {\tt has} attributes and the relationship 
between certain nodes $user$, $individual$ and $collection$ are shown.

\begin{figure*}
\captionsetup{justification=centering,margin=2cm}
\centering
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.7pt}

\fbox{\includegraphics[width=5cm,height=5cm,keepaspectratio]{img/edge_properties_has.png}}
\caption{HAS edge Properties.}
\label{fig:Has_edge}       
\end{figure*}

>>>>

  \item {\bf User-User}
  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user's preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users' preferences.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/UI_ed01.png}
    \caption{User interface of an EvoSpace-Interactive application.}
    \label{fig:web}
\end{figure}

\section{EvoSpace-Interactive}
\label{sec:evospace-i} 
As a case study, a IEA was implented using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the aplication is presented next, focusing
on the data elements that where ported to the graph model.

@@

\subsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend\'s collections by using the web interface depicted 
in Figure \ref{fig:web}.
At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
He can assign a quality assessment to the individual using
a five star rating measure.
Additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special directory to store individuals a user prefers and wishes
to save. After the user finishes interacting the individual
on the Wall, he can choose to retrieve a new one from population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

\begin{figure*}[!t]
    \centering
        \includegraphics[width=3.5in]{img/framework.png}
    \caption{IEC Human-centered framework.}
    \label{fig:web}
\end{figure*}

@@

@@

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the posibility that fitness or even part of the search 
  to be done by devices lended by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item {\bf IEC Data Model}
  A data model is used to describe the IEC system prior to a physical 
  implementation. 
  %% This block is maybe not needed but in our ES-I implementation
  %% we use Relational (PosgreSQL), Objects (JSON-Redis) and Graphs (Neo4J)
  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a Class Digram for a 
  key-value store. 
  %%
  %%
  A graph is proposed for modelling the social network
  of users and their interaction with the population. This database 
  is the back-end of the system, is used by the EA and the user interface.

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physicaly created
  the new population.  
\end{itemize}

@@

\subsection{Relationship Types}
%%
%% Explain relations

@@

The relation {\tt knows} connects two users that know each other. This relation
is "unique" meaning that it can not be repeted between a pair of nodes.  
The relation {\tt parent} describes what Individual is the parent of a new
Individual and is also unique.  
The relation {\tt has} describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  individuals stored
in them.

In figure \ref{fig:Has_edge} the {\tt has} relationship 
between certain nodes $user$, $individual$ and $collection$ is shown.

\begin{figure}[!t]
    \centering
        \includegraphics[width=2.5in]{img/edge_properties_has.png}
    \caption{ The {\tt has} relationship type example and attributes.}
    \label{fig:evo}
\end{figure}
